Persistence in functional topology: existence of persistence diagrams and Morse inequalities

### 2022-03-28 sec/introduction.tex
Reorder to address point 2 of the reviewer

Given the importance of persistence diagrams, in particular for stating and proving Morse inequalities, our focus will then be on the study of topological properties ensuring their existence for a broad class of filtered spaces and homology constructions.
For general persistence modules, a well studied condition for the existence of persistence diagrams is \emph{q-tameness} \cite{Chazal.2016a,Chazal.2016b}, which simply states that all linear maps between different real values in the persistence module have finite rank.
The motivating question can then be reformulated as asking for topological conditions on a filtered space that ensure its persistent homology to be q-tame.
We introduce two broadly applicable local-connectivity conditions and show that the first suffices for the \mbox{q-tameness} of filtrations defined by continuous functionals (\cref{t:q-tameness for continuous functions}), and the second for those defined by functionals with compact sublevel sets (\cref{t:local connectedness implies q-tameness}).

>>>>

Given the importance of persistence diagrams, in particular for stating and proving Morse inequalities, our focus will then be on the study of topological properties ensuring their existence for a broad class of filtered spaces and homology constructions.
For general persistence modules, a well studied condition for the existence of persistence diagrams is \emph{q-tameness} \cite{Chazal.2016a,Chazal.2016b}, which simply states that all linear maps between different real values in the persistence module have finite rank.
The motivating question can then be reformulated as asking for topological conditions on a filtered space that ensure its persistent homology to be q-tame.
We introduce two broadly applicable local-connectivity conditions and show that the first suffices for the \mbox{q-tameness} of filtrations defined by continuous functionals (\cref{c:q-tameness for continuous functions}), and the second for those defined by functionals with compact sublevel sets (\cref{t:local connectedness implies q-tameness}).
